What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2022-12-31 paper/main.tex
added Playing It Out section with draft bits

@@

@@

>>>>

\newcommand{\tool}{\texttt{ltl2timeline}}

@@

\section{Playing it out} %KYR: may swap order with the next section on artifact availability?

We quantify the useability and performance of \tool by compiling an extensive set of LTL formulas used in the analysis of real-life systems, defining timeline metrics, and characterizing the result of visualizing the set of all real-life LTL formulas over those metrics. We release the set of real-life LTL formulas as a benchmark set for the research community. Our experimental evaluation conclusively demonstrates that \tool scales to provide helpful visualizations of LTL formulas written by humans.

\subsection{Set of Real LTL Formulas}

We collect the LTL formulas from a covering set of publicly-available case studies that use LTL in the analysis of real-life safety-critical systems. As some formulas are redundant (i.e., common properties occur in many different case studies), it is not necessary to include every paper that has ever used LTL in a real setting; we instead opt for the largest and most unique formulas to cover the space of realistic use of LTL.

\subsection{Timeline Metrics}

Define size, length, height, complexity, etc. here.

\subsection{Experimental Analysis} %We could come up with a less-generic name for this, which would be nicer...

Here we nicely summarize (with pictures as much as possible) all of the statistics and results we gathered.

<image>
caption: For all of the <large number> of real LTL formulas historically used to analyze real systems, \tool efficiently yields useable, readable timeine visualizations.

@@

KYR: link LTL database here too.
